### 2016-08-23 notions.tex
syntax

\section{Security Notions}
\label{sec:security-notions}
\tsnote{intro text}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   
In addition to correctness, we establish three notions of privacy for
set-representations. The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\privaux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two. Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\privaux,q)$, and it must decide which set~$M$ represents.

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{\calS}{},r}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{\calS}{}$.} 
\label{fig:correctness}
\end{figure}

>>>>

\section{Security Notions}
\label{sec:security-notions}
\tsnote{intro text}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   
In addition to correctness, we establish three notions of privacy for
set-representations. The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\pubaux,\privaux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two. Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\pubaux,\privaux,q)$, and it must decide which set~$M$ represents.

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{\calS}{},r}{A}$}\\
$S \getsr \distr{\calS}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{\calS}{}$.} 
\label{fig:correctness}
\end{figure}
